\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[document]{ragged2e}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{enumitem,amssymb,graphicx}

\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
  {<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont} 

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSmall}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingBig}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
      {\small#5} & {\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{}
\renewcommand{\labelitemii}{\scalebox{0.5}{\raisebox{0.65ex}{$\blacksquare$}}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------

\textbf{\LARGE Mario Reichow}\\
Senior Software Developer\\
Düsseldorf, Germany\\\vspace{\baselineskip}
%\href{https://mwj96.dev/}{mwj96.dev}\\\vspace{\baselineskip} % <======

{\Centering % <=========================================================

\raisebox{-0.20\height}{\Large \faInbox} \space \href{mailto:mario.dornelles@gmail.com}{mario.dornelles@gmail.com} \hfill % <======
\raisebox{-0.20\height}{\Large \faPhone} \space (+49) 0176 65164272 \hfill % <======
\raisebox{-0.20\height}{\Large \faGithub} \space \href{https://github.com/markartur}{markartur} \hfill % <======
\raisebox{-0.20\height}{\Large \faLinkedinSquare} \space \href{https://www.linkedin.com/in/mario-reichow/}{mario-reichow} % <======
} % <===================================================================

%-----------EDUCATION-----------------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pontifícia Universidade Católica do Rio Grande do Sul}{Porto Alegre, Brazil}
      {B.S. Information Systems}{December 2016}	
  \resumeSubHeadingListEnd


%-----------SKILLS-----------------

\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Java, Kotlin, Python, Javascript, PHP}
    \resumeSubItem{Frameworks and Techs}
      {Node, Express, Symfony, NestJS, Typescript, Postgres, GraphQL, Kafka}
    \resumeSubItem{Cloud Experience}
      {AWS, GCP, Serverless, monitoring and tracing } 
    \resumeSubItem{Others}
      {Docker, Gitflow, Maven, JUnit, Pytest}
  \resumeSubHeadingListEnd

\renewcommand{\labelitemi}{}

%-----------EXPERIENCE-----------------

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Trivago}{Düsseldorf, Germany}
      {\textbf{Senior Software Developer}}{January 2021 -- present}
      \resumeItemListStart
        \item
          {Developed features and fixed issues in a diverse ecosystem, using technologies such as: Kotlin, PHP, NestJS, Python, Golang, Kafka, GraphQL.}
        \item
            {Designed and delivered new microservices, while mantaining more than 50 services hosted between AWS, GCP and on-premises.}
        \item
            {Spearheaded the development of cross-team projects, such as a brand new subscription product aimed at independent hoteliers .}   
        \item
            {Strived for simplification, reducing the overall number of microservices and different technologies used by the team; Greatly reducing complexity and increasing quality and cadence of deliverables.} 
        \item
            {Built a thriving software development team by recruiting, onboarding and mentoring team members.}
      \resumeItemListEnd
      
    \resumeSubheading
      {ADP}{Porto Alegre, Brazil}
      {\textbf{Senior Software Developer}}{September 2018 -- December 2020 }
      \resumeItemListStart
        \item {Helped design, build and deploy a client facing analytics tool, using Java and Oracle, developing features such as metrics and reports sharing between users and roles, and a partner module, where managers can see and manipulate metrics and dashboards from hundreds of clients.}
	\item {Traveled to India for knowledge transfer sessions, helping colleagues take ownership over a part of the system.}
        \item {Built a next generation reporting tool, with state of the art CI/CD and development practices, using Node and Java microservices within AWS cloud environment.}
      \resumeItemListEnd

    \resumeSubheading
      {ADP}{Porto Alegre, Brazil}
      {\textbf{Software Developer}}{August 2014 -- September 2018}
      \resumeItemListStart
        \item
          {Developed new features on a legacy Java Human Capital Management application, with clients on the large enterprise segment.}
        \item
          {Created and supported features for the biggest ADP client, with 150k users. Handling critical features such as hiring and payroll processing, with aggressive deadlines and compliance requirements.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Dell}{Porto Alegre, Brazil}
      {\textbf{Performance Testing Intern}}{August 2012 -- August 2014}
      \resumeItemListStart
        \item
          {Tested performance requirements on multiple applications, using both UI and API tools.}
        \item
          {Compiled and analyzed test scenario executions, identifying issues like response time bottlenecks and spikes on hardware resources.}
      \resumeItemListEnd 

\resumeSubHeadingListEnd


\end{document}
